Topological Equivariant Artist Model

### 2022-02-23 slides/main.tex
fixed broken slides

%add transition slide->possibly call back 
\subsection{Artist}
\begin{frame}
    \frametitle<0|handout:1>{Artist: \vartistc: \sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gotalc}}
    \frametitle<0|handout:2>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:3>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:4>{Artist: \vartistc: \cgamma{\opensetc}{\dtotalc} \rightarrow \cgamma{\opensetgc}{\gtotalc}}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:1>{\vindexpushc\sheafc_{\gbasec, \gtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<0|handout:1>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<0|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:1,4>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
      \end{equation*}

@@

    \onslide*<0|handout:3>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\gbasec, \dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec,\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\gbasec,\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec, \gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}   
    \end{tikzcd}
    \end{equation*}}    
    \onslide<0|handout:1>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            $\vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)$
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            $\vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)$ 
        \end{alertblock}
        }
\end{frame}

@@

\section{Equivariant Artist}
\begin{frame}{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}{Equivariant Artist}
    \begin{equation*}
    \begin{tikzcd}[ampersand replacement=\&]
        \sheafc_{\dbasec, \dtotalc} 
        \arrow[r, "\vartistc", Rightarrow, color=artist] 
        \arrow[d, "\dfuncc_{\dtotalc}"', color=action] \& 
        \sheafc_{\gbasec, \gtotalc} 
        \arrow[d, "\dfuncc_{\gtotalc}", color=action, dashed] \\
        \sheafc_{\dbasec^{\prime}, \dfuncpullc\dtotalc} 
        \arrow[r, "\vartistc", Rightarrow, color=artist]    \& 
        \sheafc_{\gbasec^{\prime},\dfuncpullc{\gbasec}\gtotalc}    
        \end{tikzcd} 
    \end{equation*}

    \begin{proposition}{}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{b})) \
        \end{align*}
    \end{proposition}
\end{frame}

\begin{frame}{Equivariant $\dfunchc$}
    \note{Maybe move to implementation section}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]
            \opensetgc 
            \arrow[rr, "\vindexc", color=functor] 
            \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
            \&  \& 
            \opensetc 
            \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
            \&  \& \\
            \opensetgc^{\prime} 
            \arrow[rr, "\vindexc"', color=functor]
            \&  \& 
            \opensetc^{\prime}\\
            \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
            \end{tikzcd}
        \end{equation*}
\end{frame}

@@

\section{Complex Structure}
\begin{frame}{Multiple Bundles: $\dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)$} 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \dfunctc_0 \dfuncpullc \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_i  \dfuncpullc \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_n \dfuncpullc \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \dfunctc_i \dfuncpullc \dtotalc 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                {(\dfunchc=\dfunchc_{i \in [0,n]})\dbasec }                                             \& \& = \& 
                \dfunchc \dbasec                                                        
                \end{tikzcd}                                              
    \end{equation*}

@@

@@

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc$ as a functor such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ \note{for all sections} 
    \end{description} 
\end{alertblock}
\end{frame}
\begin{frame}{Remapping Components}
    \begin{block}<>{Functor $\vchannel$}
        $\vchannelc$ is a functor from on fiber categories $\vchannelc: \mathcal{\dfiberc} \rightarrow \mathcal{\vfiberc}$

    \end{block}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc 
            \arrow[rr, "\vchannelc_{\dfiberc}"] 
            \arrow[rrdd, "{\vchannelc_{\dfiberc}}^{\prime}"', dotted] 
            \&  \& 
            \vfiberc \coloneqq \dfiberc^{\prime}  
            \arrow[dd, "\vchannelc_{\vfiberc}"] \\
            \&  \& \\
            \&  \& \vfiberc^{\prime}                           
        \end{tikzcd}
    \end{equation*}
\end{frame}

>>>>

%add transition slide->possibly call back 
\section{Artist}

\begin{frame}
    \frametitle<0|handout:1>{Artist: $\vartistc: \sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:2>{Data Space: $\vartistc_{\opensetc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:3>{Display Space: $\vartist_{\opensetgc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\Rightarrow} \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<0|handout:4>{Artist: $\vartistc: \cgamma{\opensetc}{\dtotalc} \rightarrow \cgamma{\opensetgc}{\gtotalc}$}

    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:1>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\gtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:1>{\vindexpushc\sheafc_{\gbasec, \gtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\vindexpushc \gtotalc\restriction_{\opensetc}}}
          \\
          \& \& \\
          \onslide*<0|handout:1>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetgc}{\vindexpullc \dtotalc\restriction_{\opensetgc}}}
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetgc}", color=artist, Rightarrow]}
          \&  \& 
          \onslide*<0|handout:1>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:4>{\cgamma{\opensetc}{\dtotalc\restriction_{\opensetc}}}
          \onslide*<0|handout:1,4>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:1,4>{\arrow[uu, "\vartistc_{\opensetc}"', color=artist, Rightarrow]}
          \onslide*<4-|handout:1,4>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, Rightarrow]}
        \end{tikzcd}
    \end{equation*}

@@

    \onslide*<0|handout:3>{
        \begin{equation*}
    \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, Rightarrow] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\gbasec, \dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec,\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc\restriction_{\opensetgc_1}} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, Rightarrow] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc\restriction_{\opensetgc_2}} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, Rightarrow] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\gbasec,\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gbasec, \gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc\restriction_{\opensetgc_2}}   
    \end{tikzcd}
    \end{equation*}}    
    \onslide<0|handout:1>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\opensetgc}(\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}, \sheafc_{\gbasec, \gtotalc}) = 
    \textcolor{nattran}{Nat}_{\opensetc}(\sheafc_{\dbasec, \dtotalc}, \textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc})
        \end{equation*}
    }
    \onslide<0|handout:4>{
        \begin{alertblock}{pull data section \dsectionc\ over graphic space $\gbasepointc \in \gbasec$}
            \begin{equation*}
                \vindexpullc\dsectionc(\gbasepointc) = \dsectionc(\vindexc(\gbasepointc)) = \dsectionc(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        \begin{alertblock}{push graphic \gsectionc\ section over data space $\dbasepointc \in \dbasec$}
            \begin{equation*}
                \vindexpushc\gsectionc(\dbasepointc) = \gsectionc\restriction_{\vindexpre(\dbasepointc)} = \gsectionc(\gbasepointc) \forall \gbasepointc \in \vindexpre(\dbasepointc)
            \end{equation*}
        \end{alertblock}
        }
\end{frame}

@@

\subsection{Equivariance}

\begin{frame}{Transform Data}
    \begin{block}{Fiber Bundle Category}
        \begin{description}[style=newline]
            \item[object] $\dfiberc \hookrightarrow \dtotalc \xrightarrow{\pi} \dbasec$
            \item[morphisms] $\dfuncc: \dtotalc \rightarrow \dtotalc$ 
        \end{description}
    \end{block}
    \begin{block}{Fiber Category}
        The fiber $\dfiberc$ is the sole object of an arbitrary category $\mathcal{C}$.
        The morphisms on the fiber are $Hom(\dfiberc, \dfiberc)$
    \end{block}

@@

\begin{frame}{Equivariant Artist}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \sheafc_{\dbasec, \dtotalc} 
            \arrow[r, "\vartistc", Rightarrow, color=artist] 
            \arrow[d, "\dfuncc_{\dtotalc}"', color=action] \& 
            \sheafc_{\gbasec, \gtotalc} 
            \arrow[d, "\dfuncc_{\gtotalc}", color=action, dashed] \\
            \sheafc_{\dbasec^{\prime}, \dfuncpullc\dtotalc} 
            \arrow[r, "\vartistc", Rightarrow, color=artist]\& 
            \sheafc_{\gbasec^{\prime},\dfuncpullc\gtotalc}
        \end{tikzcd} 
        \end{equation*}

    \begin{alertblock}{}
        \begin{align*}
            \vartistc(\dsectionc^{a}) = \vartistc(\dsectionc^{b}) &\centernot\implies \dsectionc^a = \dsectionc^b \\
            \vartistc(\dsectionc^{a})  = \vartistc(\dsectionc^{b}) &\implies \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{a})) = \vartistc(\dfuncc_{\dtotalc}(\dsectionc^{b}))
        \end{align*}
    \end{alertblock}
\end{frame}

\begin{comment}
\begin{frame}{Equivariant $\dfunchc$}
    \note{Maybe move to implementation section}
        \begin{equation*}
            \begin{tikzcd}[ampersand replacement=\&]
            \opensetgc 
            \arrow[rr, "\vindexc", color=functor] 
            \arrow[dd, "\dfunchc_{\gbasec}"', dashed, color=action] 
            \&  \& 
            \opensetc 
            \arrow[dd, "\dfunchc_{\dbasec}", color=action] \\
            \&  \& \\
            \opensetgc^{\prime} 
            \arrow[rr, "\vindexc"', color=functor]
            \&  \& 
            \opensetc^{\prime}\\
            \underbrace{\dbasec \times {[0,1]}^{m}}_{\gbasec} \arrow[rr,"\vindex", maps to, color=functor] \& \& \dbasec
            \end{tikzcd}
        \end{equation*}
\end{frame}

@@

\begin{frame}{Multiple Bundles: $\dfuncc = (\dfunchc, \prod\limits_{i=0}^{n}\dfunctc_i)$} 
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement = \&, column sep=2ex]
                \dfunctc_0 \dfuncpullc \dtotalc_0 
                \arrow[rdd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_i  \dfuncpullc \dtotalc_i 
                \arrow[dd, "\pi" description] 
                \arrow[r, "\cdots \otimes \cdots", phantom] \& 
                \dfunctc_n \dfuncpullc \dtotalc_n 
                \arrow[ldd, "\pi" description] \& = \& 
                \prod\limits_{i=0}^{n} 
                \dfunctc_i \dfuncpullc \dtotalc 
                \arrow[dd, "\pi" description] \\    
                \&\&\&\&\\    
                \& 
                {(\dfunchc=\dfunchc_{i \in [0,n]})\dbasec }                                             \& \& = \& 
                \dfunchc \dbasec                                                        
                \end{tikzcd}                                              
    \end{equation*}

@@

\begin{frame}{Functor $\vchannelc: \dfiberc \rightarrow \vfiberc$}
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
            \dfiberc 
            \arrow[rr, "\vchannelc_{\dfiberc,\vfiber}"] 
            \arrow[rrdd, "{\vchannelc_{\dfiberc,{\vfiberc}^{\prime}}"', dotted] 
            \&  \& 
            \vfiberc \coloneqq \dfiberc^{\prime}  
            \arrow[dd, "\vchannelc_{{\dfiberc}^{\prime}, {\vfiberc}^{\prime}}"] \\
            \&  \& \\
            \&  \& \vfiberc^{\prime}                           
        \end{tikzcd}
    \end{equation*}
    \begin{alertblock}
        $\vchannelc$ is a functor s.t. if there exists a map ${\vchannelc}_{\dfiber, \vfiber}: \dfiber \mapsto \vfiber$ and 
        ${\vchannelc}_{{\dfiber}^{\prime}, {\vfiber}^{\prime}}: {\dfiber}^{\prime} \mapsto {\vfiber}^{\prime}$ then by composition there exists a map ${\vchannelc}_{\dfiberc, {\vfiberc}^{\prime}}: \dfiberc \rightarrow {\vfiberc}^{\prime}$
    \end{alertblock}
\end{frame}

@@

    \begin{alertblock}{Build in Equivariance}
    implement $\vchannelc$ as a functor such that 
        \begin{description}
            \item[equivariance] $\vchannelc(\dfuncc_{\dtotalc}(\dsectionc(\dbasepointc))) = \dfuncc_{\vtotalc}(\vchannelc(\dsectionc(\dbasepointc)))$, for all $\dbasepointc \in \dbasec$ 
            \item[continuity] $\lim\limits_{x\to \dbasepointc}(\vchannelc(\dsectionc(x))) = \vchannelc(\dsectionc(\dbasepointc))$ for all $\dbasepointc \in \dbasec$ \note{for all sections} 
    \end{description} 
\end{alertblock}
\end{frame}
